Towards a Cognitive System That Can Recognize Spatial Regions Based on Context

### 2012-01-25 scenarios/cdsr/trunk/papers/AAAI2012/main-aaai12-cdsr.tex

\begin{figure}[h]
  \includegraphics[width=\columnwidth]{images/AnalogyDiagram.png}
  \caption{Analogical mapping between five base expressions and three target expressions. }
  %Ovals and squares represent relations and entities respectively. Black dashed bi-directional arrows are the correspondences between the base and target, and the red dashed objects represent a candidate inference projected into the target.

@@

Figure \ref{fig:analogy} illustrates a sample mapping between five base expressions and three target ones. Each oval represents a binary predicate, and its two entity arguments are represented by squares. SME generates a mapping between the base expressions \fw{(group Desk1 Desk2)} and  \fw{(xMinusYZero Desk1 Desk2)}, and the  target expressions \fw{(group Desk11 Desk12)} and \fw{(xMinusYZero Desk11 Desk12)} as well as between the \fw{regionType} expressions in each case . This is done in the following manner. First, the predicates of these expressions are placed in correspondence, as identical predicates are preferred by SME. Additional align the arguments of the aligned predicates, \fw{Desk1} with \fw{Desk11},  \fw{Desk2} with \fw{Desk12}, and \fw{CDSR1} with \fw{CDSR2}. While there is another \fw{XMinusYZero} statement in the base about two desks, it cannot correspond to either of the target expressions in the same mapping due to the one-to-one constraint in SME which allows each element in the target to map to at most one element in the base and vice versa. In Figure \ref{fig:analogy}, the correspondences are highlighted by the hashed bi-directional arrows. Next, SME creates a candidate inference for the region boundary expression, because both the mapped \fw{Group} and \fw{regionType} predicates participate in the mapping. The candidate inference is stated as \fw{(regionBoundary(:skolem CSDR1) (XMinYMost ...))}. \fw{:skolem} is used to denote entities that do not exist in the target description but are included in the candidate inferences. In this case, the candidate inference states that there is something like \fw{CSDR1} in the target, and its boundary includes the \fw{XMinYMost} point of the two desk group. Note that inference is selective, with no candidate inferences generated for the entirely unmapped expressions. %Next, we describe how we use the results of an analogy to infer a context-dependent spatial region in the target.

>>>>

\begin{figure}[h]
  \includegraphics[width=\columnwidth]{images/AnalogyDiagram.png}
  \caption{Analogical mapping between six base expressions and three target expressions. }
  %Ovals and squares represent relations and entities respectively. Black dashed bi-directional arrows are the correspondences between the base and target, and the red dashed objects represent a candidate inference projected into the target.

@@

Figure \ref{fig:analogy} illustrates a sample mapping between six base expressions and three target ones. Each oval represents a binary predicate, and its two entity arguments are represented by squares. SME generates a mapping between the base expressions \fw{(group Desk1 Desk2)} and  \fw{(xMinusYZero Desk1 Desk2)}, and the  target expressions \fw{(group Desk11 Desk12)} and \fw{(xMinusYZero Desk11 Desk12)} as well as between the \fw{regionType} expressions in each case . This is done in the following manner. First, the predicates of these expressions are placed in correspondence, as identical predicates are preferred by SME. Additional align the arguments of the aligned predicates, \fw{Desk1} with \fw{Desk11},  \fw{Desk2} with \fw{Desk12}, and \fw{CDSR1} with \fw{CDSR2}. While there is another \fw{XMinusYZero} statement in the base about two desks, it cannot correspond to either of the target expressions in the same mapping due to the one-to-one constraint in SME which allows each element in the target to map to at most one element in the base and vice versa. In Figure \ref{fig:analogy}, the correspondences are highlighted by the hashed bi-directional arrows. Next, SME creates a candidate inference for the region boundary expression, because both the mapped \fw{Group} and \fw{regionType} predicates participate in the mapping. The candidate inference is stated as \fw{(regionBoundary(:skolem CSDR1) (XMinYMost ...))}. \fw{:skolem} is used to denote entities that do not exist in the target description but are included in the candidate inferences. In this case, the candidate inference states that there is something like \fw{CSDR1} in the target, and its boundary includes the \fw{XMinYMost} point of the two desk group. Note that inference is selective, with no candidate inferences generated for the entirely unmapped expressions. %Next, we describe how we use the results of an analogy to infer a context-dependent spatial region in the target.
